On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-03-25 paper_arxiv/arxiv_cav_determinisim_main.tex
updating text, authorship

\author{Greg Chance\inst{1,3}, Abanoub Ghobrial\inst{1,3}, Kevin McAreavey\inst{1,3}, Severin Lemaignan\inst{2,3}, Tony Pipe\inst{2,3}, Kerstin Eder\inst{1,2}}

\authorrunning{A. Ghobrial et al.}
\institute{University of Bristol, Bristol, UK \and University of the West of England, Bristol, UK \and Bristol Robotics Laboratory, Bristol, UK}
\tocauthor{Authors' Instructions}
\maketitle

>>>>

\author{Greg Chance\inst{1,3}, Abanoub Ghobrial\inst{1,3}, Kevin McAreavey\inst{1,3}, S\'everin Lemaignan\inst{2,3}, Tony Pipe\inst{2,3}, Kerstin Eder\inst{1,2}}

\authorrunning{G. Chance, A. Ghobrial et al.}
\institute{University of Bristol, Bristol, UK \and University of the West of England, Bristol, UK \and Bristol Robotics Laboratory, Bristol, UK}
\tocauthor{Authors' Instructions}
\maketitle
